Cryptographic assurance of secrecy and fairness in voting

### 2012-12-07 paper/paper.tex
Add note about random candidate ordering providing voter privacy.
Add scantegrity image

\todo{Include our own depiction of the tables in an image.}

@@

\todo{Discuss variants (decryption mixnets, reencryption mixnets) on how to generate the encrypted permutations.}

@@

\todo{Tallying the vote}

\todo{Fill in.}

@@

Scantegrity relies on unused \term{audit ballots} to prove that its Tables Q, R, and S accurately
match ballot selections with the proper candidates. These ballots come in two forms: a group of
ballots randomly selected and checked prior to the election by members of the election authority;
and the collection of optional secondary ballots that are offered to voters.

Auditing is then performed by revealing all bubble codes on the ballots and uncovering the entire
R-to-S mapping in Table Q for all rows corresponding to those revealed codes. An auditor then
manually examine the revealed information and ensure that, had a code been revealed as on a counted
ballot, the tally would have been affected appropriately. Note that this method of verification is
indirect in that it does not allow \emph{any} of the ballots that are cast during the election to be
verified, for reasons previously stated. Rather, it is expected that the random selection of ballots
beforehand, along with the selection of ballots chosen by voters as audit ballots, is a sufficient
sample to detect improper counting. Thus, if these checks past, it is accepted that all other
ballots must also be counted properly.

@@

In some ways, count verification is simpler than that in Scantegrity. We have already discussed how
Helios uses a mixnet to achieve ballot secrecy. Once votes have been mixed using this mechanism,
they are decrypted, and so the actual plaintext ballots are exposed. From that point, tallying is
straightforward.

>>>>

\begin{figure}
	\center
	\includegraphics[width=\columnwidth]{images/include/scantegrity.pdf}
	\caption{
		Visualization of links between Scantegrity tables.
		Lines represent pointers in Table R.
		Dashed lines represent secret (unpublished) values.
	}
	\label{fig:scantegrity}
\end{figure}

@@

Presenting candidates in a different, random order on each ballot conceals the voter's choice of candidates, as long as the process of decrypting the vote hides the correlation between ballot and voter (see below).

\todo{Discuss variants (decryption mixnets, reencryption mixnets) on how to generate the encrypted permutations ?????}

@@

Once all votes have been cast and recorded, the election authority mixes, decrypts, and tallies the votes to determine the winners while maintaining ballot secrecy.
Mixing the encrypted votes before or during the decryption process (depending on the \pv\ variant) ensures the votes remain anonymous, even to the officials performing the encryption, by preventing discovery of any match between a particular encrypted vote and its decrypted counterpart.

\pv\ accomplishes this process via a \term{mixnet}: a set of mix servers each secretly shuffle and transform, in turn, the set of encrypted votes in a verifiable way. Scratch \& Vote \cite{scratch}, a variation on \pv, tallies the votes homomorphically rather than with a mixnet.

@@

One source of vote auditing in Scantegrity relies on unused \term{audit ballots} to prove that its
Tables Q, R, and S accurately match ballot selections with the proper candidates. These ballots come
in two forms: a group of ballots randomly selected and checked prior to the election by members of
the election authority; and the collection of optional secondary ballots that are offered to voters.

This auditing is then performed by revealing all bubble codes on those audit ballots and uncovering the
entire R-to-S mapping in Table Q for all rows corresponding to those revealed codes. An auditor then
manually examines the revealed information to ensure that, had a code been revealed as on a counted
ballot, the tally would have been affected appropriately.

Secondly, recall that for each row in Table R that does not represent an audit ballot, only half of
the Q-to-S mapping is revealed; \emph{which} half is uncovered is chosen randomly. This prevents an
auditor from mapping any cast ballot to its chosen candidate, but it permits \emph{partial}
verification by allowing an observer to note that the following are true:
\begin{itemize}
	\item
		If a row in Table R is \textbf{checked} and its mapping to Table Q is revealed, then the
		corresponding cell in Table Q has a \textbf{revealed} confirmation code (indicating that the
		code was revealed on a ballot).
	\item
		If a row in Table R is \textbf{unchecked} and its mapping to Table Q is revealed, then the
		corresponding cell in Table Q has a \textbf{hidden} confirmation code (indicating that the code
		was \emph{not} revealed on a ballot).
	\item
		If a row in Table R is \textbf{checked} and its mapping to Table S is revealed, then the
		corresponding cell in Table S is \textbf{checked} (indicating an addition to a candidate's
		tally).
	\item
		If a row in Table R is \textbf{unchecked} and its mapping to Table S is revealed, then the
		corresponding cell in Table S is \textbf{unchecked} (indicating \emph{no} addition to a
		candidate's tally).
\end{itemize}
This technique -- verifying a random partial sample of the data -- is called \term{random partial
checking}. If these checks past, it is accepted that all other ballots must also be counted properly.

@@

In some ways, Helios count verification is simpler than that in Scantegrity. We have already
discussed how Helios uses a mixnet to achieve ballot secrecy. Once votes have been mixed using this
mechanism, they are decrypted, and so the actual plaintext ballots are exposed. From that point,
tallying is straightforward.
